refnx - Neutron and X-ray reflectometry analysis in Python

### 2018-07-17 paper/manuscript.tex
PAPER: small change

\section*{Comments on reproducibility of analyses}
In order for a given scattering analysis to be fully reproducible by others a general set of conditions need to be met:
\begin{itemize}
  \item the datasets used need to be deposited with a journal article, or be freely available.
  \item the exact software environment needs to be recreateable.
  \item the exact ordered set of steps taken during the analysis needs to be listed.
\end{itemize} 
Each of these points are frequently neglected. For example, the use of different software versions may change the output from an analysis. The use of a GUI program may not record the full set of steps, or options, applied by a user.
Whilst it is unable to meet the first criteria by itself the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken. The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc). At a later date those exact versions can be installed in the same Python version using one of: the \conda package manager, by installing from the source at a given version tag in the git repository, or by \pip. \conda can use environment files to recreate a specific setup. An alternative way of recreating the environment is a virtual machine, such as Docker.
The usefulness of open-source software in a git repository must be emphasised here - the ability to return to a specific software version/environment is often difficult with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis. This has important implications for verifiability.
%TODO finish verifiability...  Open source - the user can look at the code for correctness, with unit testing we can see if things are calculated correctly. With closed source we have no idea if there are major problems with certain parts of an algorithm.
%\refnx relies on a fully open software stack, with full traceability of every single line of code.

>>>>

\section*{Comments on reproducibility of analyses}
In order for a given scattering analysis to be fully reproducible by others a general set of conditions need to be met:
\begin{itemize}
  \item the datasets used need to be deposited with a journal article, or be freely available.
  \item the exact software environment needs to be recreateable.
  \item the exact ordered set of steps taken during the analysis needs to be listed.
\end{itemize} 
Each of these points are frequently neglected. For example, the use of different software versions may change the output from an analysis, or the use of a GUI program may not record the full set of steps, or options, applied by a user.
Whilst it is unable to meet the first criteria by itself the use of \refnx in a \Jupyter notebook can fulfil the other two requirements, providing a little care is taken. The exact software environment can be recreated by noting down the versions of the software packages used during an analysis (\refnx, \SciPy, \NumPy, Python, etc). At a later date those exact versions can be installed in the same Python version using one of: the \conda package manager, by installing from the source at a given version tag in the git repository, or by \pip. \conda can use environment files to recreate a specific setup. An alternative way of recreating the environment is a virtual machine, such as Docker.
The usefulness of open-source software in a git repository must be emphasised here - the ability to return to a specific software version/environment is often difficult/impossible with proprietary or closed source software; different versions can have modifications that can significantly change the output of an analysis. This has important implications for verifiability.
%TODO finish verifiability...  Open source - the user can look at the code for correctness, with unit testing we can see if things are calculated correctly. With closed source we have no idea if there are major problems with certain parts of an algorithm.
%\refnx relies on a fully open software stack, with full traceability of every single line of code.
